\quad The purpose of the Students \& Companies (S\&C) platform is to provide a centralized, user-friendly environment where university students can search for internship opportunities and where companies can advertise their offers. By consolidating internship advertisements in one place, the platform allows students to easily compare opportunities based on criteria such as required skills, offered benefits, and other terms. It ensures a safe and transparent process, minimizing the risk of exploitation by providing mechanisms for university supervision and feedback. Companies benefit from the platform’s reach, enabling them to connect with a broad pool of talented students efficiently. In addition, the platform fosters trust by ensuring university oversight, making it a reliable space for students and companies to interact.

\subsubsection{Goals}
\begin{itemize}
    \item \textbf{[G1]} Companies create internship advertisement.
    \item \textbf{[G2]} Students find appropriate internship and initiate contact with the selected company.
    \item \textbf{[G3]} Students become interns in the companies in order to gain experience in the desired area of industry.
    \item \textbf{[G4]} The platform provides a transparent and fair selection process where companies can evaluate and select suitable candidates.
    \item \textbf{[G5]} The platform offers a recommendation system that matches students to internships based on their CVs, skills, and preferences, as well as company requirements.
    \item \textbf{[G6]} The platform allows universities to monitor internships to ensure alignment with academic standards.
    \item \textbf{[G7]} The platform collects feedback from both students and companies to improve the platform’s functionality.
    \item \textbf{[G8]} Ensure a safe and supportive environment by providing students with mechanisms to file complaints and enabling universities to resolve them.
    
\end{itemize}