Users that are present on the platform and interact are: \textit{Student}, \textit{Company} and \textit{University}. This section presents their needs which are satisfied by the platform.

%\subsubsection{Administrator}
%User \textit{Administrator} has a role in enabling the proper functioning of the platform and addressing any system-level issues. Key duties include managing user accounts by approving or suspending registrations for companies and universities, monitoring platform performance, and maintaining data integrity and privacy. Administrators handle escalated complaints from universities, and oversee system updates, bug fixes, and feature enhancements. Additionally, administrators provide technical support, generate activity reports, and communicate critical updates or announcements to users.


\subsubsection{Student}
User \textit{Student} has an option to sign up and login in order to access the platform. On the platform the student can search for the internships and apply for them. The student can be shortlisted or declined. If the student is shortlisted, he continues with the selection process which results with admission to the internship or rejection. The student has a possibility to file a complaint if the selection process or an active internship is not as described in the advertisement or are not by academic or ethical practices.


\subsubsection{Company}

User \textit{Company} is, as the student, can sign up and login in order to access the platform. When logged in, the company can create and manage an advertisement for an internship role that is open. Company is able to manage the selection process and guide students through it. Also, the company may file a complaint if the internship progress is not as expected due to student misbehaviour. 



\subsubsection{University}
User \textit{University} is responsible for monitoring and supervising the process of selection and progress of the active internships. The university user are able to sign up and log in to the platform. In addition, this user has to handle complaint requests by students and companies. 

