\subsubsection{Regulatory policies}

The S\&C platform operates within the framework of applicable local laws and regulations about employment and internships. It follows labor laws that protect interns from exploitation in Italy, ensuring fair compensation and working conditions. The platform complies with data protection regulations, such as GDPR, by securing user data and limiting access to authorized personnel. Companies must ensure that the internships meet employment standards and are according to anti-discrimination policies. Universities play a regulatory role by monitoring internships to ensure ethical practices and compliance with academic requirements.
%Change the text a little bit??

\subsubsection{Domain assumptions}

The following domain assumptions are needed in order for the platform to work successfully. 

\begin{itemize}
    \item \textbf{[D1]} User must have a reliable internet connection.
    \item \textbf{[D2]} All users provide accurate information when creating profiles.
    \item \textbf{[D3]} Universities actively engage with the platform in order to monitor active internships and to resolve complaints.
    \item \textbf{[D4]} Companies provide accurate information about an internship.
    \item \textbf{[D5]} The system will be available ensuring uninterrupted access to users.
    \item \textbf{[D6]} Submitted complaints are genuine and not misused to create unnecessary conflicts.
    \item \textbf{[D7]} Companies respond to applications promptly.
    \item \textbf{[D8]} Students complete selection process steps within deadlines.
\end{itemize}