

\newcounter{reqCounter} % Define a custom counter for functional requirements
\stepcounter{reqCounter}

Within this section can be found a list of functional requirements for S\&C, categorized by the major features of the platform.

\paragraph{Registration of Students}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall allow new student users to register on the platform using their respective institutional accounts.
    \item \stepcounter{reqCounter} After an institutional account has been linked with the platform, the system shall allow student users to log in using their institutional credentials.
    \item \stepcounter{reqCounter} The system shall allow the registration of student users only if they are classified as students within the institutional account they provide.
\end{itemize}

\paragraph{Registration of Companies}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall allow new company users to register on the platform using a valid email address.
    \item \stepcounter{reqCounter} After providing an email address, the system shall verify the provided address through a verification email.
    \item \stepcounter{reqCounter} After the new company user has verified their email, the system shall generate and deliver a password for the newly created account via the verified email.
    \item \stepcounter{reqCounter} The system shall allow the company user to log in using the validated email address and the provided password.
    \item \stepcounter{reqCounter} Upon the first login, the system shall require the new user to provide a certificate from the relevant tax authority, including the company name and unique identifier. The system shall also require the full company name and unique identifier to be entered manually in the relevant input fields alongside the certificate.
    \item \stepcounter{reqCounter} The system shall retain company user data only at two points: first, after successful email verification, where the provided email address and generated password will be retained as login credentials; and second, after submitting the initial verification information, where all submitted data up to that point shall be retained.
\end{itemize}



\paragraph{Registration of Universities}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall allow new university users to register on the platform using pre-designated institutional accounts allocated for S\&C.
    \item \stepcounter{reqCounter} After an institutional account has been linked with the platform, the system shall allow university users to log in using their institutional credentials.
    \item \stepcounter{reqCounter} If the institutional account has not been pre-designated for use on S\&C, the system shall reject the registration attempt.
\end{itemize}

\paragraph{Profile Management}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall, by default, provide a blank profile template for all users.
    \item \stepcounter{reqCounter} The system shall provide different collections of predetermined fields based on the user type.
    \item \stepcounter{reqCounter} The system shall allow all users to edit each field in their profile, with the exception of unique identifiers, such as tax numbers for companies and universities, and unique IDs for students, which cannot be altered.
    \item \stepcounter{reqCounter} The system shall allow each field to be configured as public or private, provided that data is present in the respective field.
    \item \stepcounter{reqCounter} The system shall automatically configure all fields with no data as private.
    \item \stepcounter{reqCounter} The system shall allow all users to provide public hyperlinks to other platforms which the system shall display in a format that clearly indicates the platform to which the hyperlink leads to.
    \item \stepcounter{reqCounter} The system shall integrate OpenAI's ChatGPT 4.0 API into each field to provide AI-generated suggestions for profile improvements.
\end{itemize}



\paragraph{Internship Advertisement Creation and Management}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall only allow company users whose data has been verified to create, update, and delete public internship advertisements, where the system shall save unfinished advertisements as draft.
    \item \stepcounter{reqCounter} The system shall allow the creation of new internship advertisements only if they possess the following fields: name, internship duration, short description, location, internship type, and the number of stages in the application process.
    \item \stepcounter{reqCounter} The system shall integrate OpenAI's ChatGPT 4.0 API into each field of the internship advertisement creation process to provide AI-generated suggestions for enhancing the advertisement.
    \item \stepcounter{reqCounter} The system shall allow for numerous types of stages to be created, including but not limited to questionnaires and video interviews, which may be scheduled on external platforms.
   
    \item \stepcounter{reqCounter} Should the internship creation process be interrupted at any stage, the system shall save the unfinished internship advertisement as a draft.
    \item \stepcounter{reqCounter} After creation, the system shall allow company users to make updates to all fields of each internship advertisement they have created, with the exception of that internship advertisement's unique ID and publication timestamp.
\end{itemize}

\paragraph{Internship Search, Application, and Management of Applications}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} The system shall analyze the profile of the student user upon login and recommend 3 internship advertisements based on matching qualifications and background, and display these recommendations prominently to the student user.
    \item \stepcounter{reqCounter} The system shall allow student and university users to view all internship advertisements posted by any company on the platform, not just those they are applying to. Company users, however, will only be allowed to view and manage the advertisements they have created.
    \item \stepcounter{reqCounter} The system shall allow all student users to apply to internship advertisements, after which their profiles will be automatically inserted into the list of applicants under the Stage 1 category.
    \item \stepcounter{reqCounter} Upon a successfully submitted application, the system shall notify the advertisement's creator.
    \item \stepcounter{reqCounter} The system shall only allow company users who are creators of the internship advertisement to move candidates further along the selection stages.
    \item \stepcounter{reqCounter} The system shall allow the company user, at any given stage, to reject any candidate without mandating a reason.
    \item \stepcounter{reqCounter} Upon a change in status, be it a rejection or a move up in the selection stages, the system shall always notify the candidate of the change.
    \item \stepcounter{reqCounter} Upon reaching the final stage as designated by the company, the system shall automatically classify the candidate as accepted for the internship.
    \item \stepcounter{reqCounter} The system shall allow the company user to request the commencement of an internship from the candidate's host university. After the internship is approved by the host university, it shall commence on a predetermined date.
\end{itemize}

\paragraph{Internship Monitoring \& Complaint Management}
\begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
    \item \stepcounter{reqCounter} During any stage of the internship, the system shall allow both the candidate and the company user to submit a complaint to the host university, after which the university user shall be automatically notified.
    \item \stepcounter{reqCounter} After a complaint is received, the university may choose to resolve the complaint or to terminate the internship. The system shall allow for both choices to be submitted.
    \item \stepcounter{reqCounter} The system shall not allow the termination of an internship by any party except the university user. The system shall allow a termination only after a complaint has been submitted.
\end{itemize}

% Ovo su NFRs koje sam izfiltrirao iz orginalnih FRs, koje cu dodat kasnije. Ovdje stoje samo kao note.
% \paragraph{NFRs}
% \begin{itemize}[label={[\textbf{FR\arabic{reqCounter}}]}, align=left, leftmargin=*]
%     \item \stepcounter{reqCounter} The system shall not retain any user data unless the student user registration process is fully completed.
%     \item \stepcounter{reqCounter} For company validation, the system shall exclusively accept files in the .pdf format for the initial company verification document. The system shall validate the file format and ensure that the file size does not exceed 10 MB.
%     \item \stepcounter{reqCounter} The system shall not retain any user data unless the registration process is fully completed. - Uni registartion
%     \item \stepcounter{reqCounter} The system shall take snapshots every 10 seconds during the internship advertisement creation process, where all filled fields will be saved. - Ad creation
%     \item \stepcounter{reqCounter} A submitted complaint has a maximum waiting period of 14 calendar days, after which the system shall automatically terminate the internship.
%     \item \stepcounter{reqCounter} The system shall automatically filter all text inserted in user fields for profanities. - Profile Management
%     \item \stepcounter{reqCounter} After the new company user has verified their email, the system shall generate and deliver a password with a minimum length of 32 characters, including a randomized combination of uppercase letters, lowercase letters, numbers, and special characters, for the newly created account via the verified email.
%     \item \stepcounter{reqCounter} The system shall ensure that the input field accepts only string-type inputs, with all Unicode characters supported. The system shall validate the input in real-time and reject non-string data types.
%     \item \stepcounter{reqCounter} Unless otherwise specified by the company, the system shall, by default, assign a 21-calendar-day duration for which the advertisement will be publicly viewable.
%     \item \stepcounter{reqCounter} The system shall not allow advertisements to be visible for more than 90 calendar days.
%     \item \stepcounter{reqCounter} The system shall, by default, provide the internship advertisements in batches of 10, with the most recent advertisements presented at the top of the list.
%     \item \stepcounter{reqCounter} The system shall provide an appropriate error message if the registration process is interrupted at any stage, specifying the reason for the interruption.
%     \item \stepcounter{reqCounter} The system shall provide an appropriate error message if the registration process is interrupted at any stage, specifying the reason for the interruption.
%     \item \stepcounter{reqCounter} The system shall provide an appropriate error message if the process is interrupted at any stage, specifying the reason for the interruption. The level of data retention will depend on the stage the user has reached before the interruption, as specified in [FR13].
% \end{itemize}




\subsubsection{Use cases Diagram}
\subsubsection{Use cases}
\subsubsection{Requirement mapping}
