\subsubsection{Reliability}
During development, the entire platform will be subject to rigorous testing to ensure that all features are working as described with no variations. Moreover, as the application will be dockerized and deployed using AWS, it should ensure that should whichever instance of the platform experience issues, a new instance can be deployed instantly (should it be needed). 
\subsubsection{Availability}
Deploying on AWS ensures an availability metric between 99.80\% and 99.99\%, even with issues such as cyber attacks or platform updates. As mentioned, most user activities will be subject to snapshots and draft-saving, hence, in the unlikely event of the platform going offline, users will be able to return to their activities precisely where they left off.
\subsubsection{Security}
Beyond following all the necessary privacy laws, the platform shall follow the highest possible security standards along with best practices as three different user groups with extremely sensitive data are at stake. Multi Factor Authentication shall be mandatory for all users and to end data encryption will be a minimum for all users, strong measures against data scraping shall be taken, a zero-trust architecture will be employed, and privacy by design will be the standard moving forward.
\subsubsection{Maintainability}
The software platform will be subject to the use of extensive testing and code analysis software. Technical debt shall be avoided at all costs, and monthly refactoring shall be a regular occurrence. Moreover, atomicity shall be forced for each software component, with test coverage being at 95\% at all time without exception.
\subsubsection{Portability}
S&C is designed to be cross-platform, allowing access from virtually any device capable of processing JavaScript. In terms of porting the system to a different service provider, or moving to private hosting - the platform will benefit heavily from containerization and virtualization, therefore, transferring the client side application as well as any backend functionality to any other service should not prove to be an issue. Moreover, as identical backups of the database shall be created in real-time, migrating the database will be a straight-forward process with graceful database migration.
